### 2020-11-23 README.Rmd
New data files, and have added a working example in the Readme.

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the resdir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
resdir <- paste0(ddir,"aMSEUse/conddata/generic2")  # data and results directory
dirExists(resdir,make=TRUE,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, zone1.csv
# and region1.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate(),
# and zonefiletemplate.  In the meantime it is easier to use the included 
# data files. The original csv files are included in the data-raw directory

# Many changes now require the data files to be updated and tested, but that will 
# happen soon.

>>>>

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the resdir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
resdir <- paste0(ddir,"aMSEUse/conddata/generic")  # data and results directory
dirExists(resdir,make=TRUE,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# In the meantime it is easier to use the included data file "zone".
data(zone)
# Of course, usually one would use data files, control.csv and a zone.csv, which is 
# listed as the datafile within the control.csv. 
# zone <- makeequilzone(resdir,"control2.csv") # normally would read in a file
    equiltime <- (Sys.time())   # let's change the initial depletion
    origdepl <-  c(0.30,0.31,0.29,0.32,0.30,0.31,0.29,0.32) 
zoneDD <- depleteSAU(zone$zoneC,zone$zoneD,zone$glb,origdepl,zone$product,len=12)
out <- prepareprojection(zone$zone1,zone$zoneC,zone$glb,zoneDD,zone$ctrl)
  zoneDR <- out$zoneDP
  projC <- out$projC
  zoneCP <- out$zoneC
  midtime <- (Sys.time())

  glb <- zone$glb
  ctrl <- zone$ctrl
  print(equiltime - starttime)
  print(midtime - equiltime)
  propD <- getzoneprops(zone$zoneC,zoneDD,glb,year=1)
  # round(propD,3)
# Do the replicates ------------------------------------------------------------
  inityr <- zone$zone1$projC$inityrs
  saunames <- zone$zone1$SAUnames
  sauindex <- zone$glb$sauindex
  pyrs <- projC$projyrs + projC$inityr
  B0 <- tapply(sapply(zone$zoneC,"[[","B0"),sauindex,sum)
  exB0 <- tapply(sapply(zone$zoneC,"[[","ExB0"),sauindex,sum)

  midtime <- (Sys.time())
mseproj <- applymcda(zoneCP,zoneDR,glb,ctrl,projC$projyrs,projC$inityrs)
sauzoneDP <- asSAU(mseproj,sauindex,saunames,B0,exB0)
  endtime <- (Sys.time())
  print(endtime - midtime)
# Now plot some results
  plotC <- function(nsau,saunames,reps,projyrs,plts=c(4,2)) {
    return(list(nsau=nsau,saunames=saunames,reps=reps,projyrs=projyrs,plts=plts))
  }

  saunames <- zone$zone1$SAUnames
  pyrs <- projC$projyrs + projC$inityr
  reps <- ctrl$reps
  label <- "Catches t"
  yrs <- 1:pyrs

plotconst <- plotC(nsau=length(saunames),saunames,reps,pyrs,plts=c(4,2))

plotprep(width=7,height=8,newdev=FALSE)
plotproj(sauzoneDP$cpue,"CPUE",plotconst,vline=projC$inityrs,addqnts=TRUE)

plotproj(sauzoneDP$saudeplsB,"Spawning Biomass Depletion",plotconst,vline=projC$inityrs,addqnts=TRUE)

plotproj(sauzoneDP$recS/1000,"Recruitment '000s",plotconst,vline=projC$inityrs,addqnts=TRUE)

plotproj(sauzoneDP$catS,"Catches t",plotconst,vline=projC$inityrs,addqnts=TRUE)
